---
title: "Two"
author: "David Stroud"
date: "2/15/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo =TRUE)
```

```{r}
# get the require R packages
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(MASS)
library(dplyr)
library(lars)
library(moments)
library(caret)
library(corrplot)
library(gbm)
```

```{r}
# load the datasets
train <- read.csv("train.csv")
test <- read.csv("test.csv")
summary(train)
str(train)
```

```{r}
ggplot(train,aes(y=SalePrice,x=GrLivArea)) +
  geom_point(
  color="red",
  fill="blue",
  shape=21,
  alpha=0.5,
  size=2,
  stroke=1
)
```

When we compare SalePrice and GrLivArea, we see that there are four outliers. To prevent overfitting, we will will remove them from the training set.

```{r}
train <- train[train$GrLivArea<=4000,]
```

```{r}
Missing_indices <- sapply(train,function(x)sum(is.na(x)))
Missing_Summary <- data.frame(index = names(train),Missing_Values=Missing_indices)
Missing_Summary[Missing_Summary$Missing_Values > 0,]
```

The chart above shows the amount of missing values in the training dataset. When we reference the data_description for the project, notice that NA can stand for something other than Non Applicable. This is the case with respect to the basement as well as the Fireplace in the basement. We will make the changes to the respective data by substituing None for missing value instead of NA.


```{r}
# combine the test and train data
test$SalePrice <- NA
train$isTrain <- 1
test$isTrain <- 0
combined <- rbind(train,test)
```

The training and testing data have been combined to make the data easier to manage. 


```{r}
combined$MasVnrArea[which(is.na(combined$MasVnrArea))] <- mean(combined$MasVnrArea,na.rm=T)
```


```{r}
# Changing NA in Alley to None
combined$Alley1 <- as.character(combined$Alley)
combined$Alley1[which(is.na(combined$Alley))] <- "None"
table(combined$Alley1)
combined$Alley <- as.factor(combined$Alley1)
combined <- subset(combined,select = -Alley1)
# Changing NA in MasVnrType to None
combined$MasVnrType1 <- as.character(combined$MasVnrType)
combined$MasVnrType1[which(is.na(combined$MasVnrType))] <- "None"
combined$MasVnrType <- as.factor(combined$MasVnrType1)
combined <- subset(combined,select = -MasVnrType1)
table(combined$MasVnrType)
# Imputing missing Lot Frontage by the median
combined$LotFrontage[which(is.na(combined$LotFrontage))] <- median(combined$LotFrontage,na.rm = T)


# Changing NA in FireplaceQu to None
combined$FireplaceQu1 <- as.character(combined$FireplaceQu)
combined$FireplaceQu1[which(is.na(combined$FireplaceQu))] <- "None"
combined$FireplaceQu <- as.factor(combined$FireplaceQu1)
combined <- subset(combined,select = -FireplaceQu1)

# Changing NA in PoolQC to None
combined$PoolQC1 <- as.character(combined$PoolQC)
combined$PoolQC1[which(is.na(combined$PoolQC))] <- "None"
combined$PoolQC <- as.factor(combined$PoolQC1)
combined <- subset(combined,select = -PoolQC1)

# Changing NA in Fence to None
combined$Fence1 <- as.character(combined$Fence)
combined$Fence1[which(is.na(combined$Fence))] <- "None"
combined$Fence <- as.factor(combined$Fence1)
combined <- subset(combined,select = -Fence1)

# Changing NA in MiscFeature to None
combined$MiscFeature1 <- as.character(combined$MiscFeature)
combined$MiscFeature1[which(is.na(combined$MiscFeature))] <- "None"
combined$MiscFeature <- as.factor(combined$MiscFeature1)
combined <- subset(combined,select = -MiscFeature1)

# Changing NA in GarageType to None
combined$GarageType1 <- as.character(combined$GarageType)
combined$GarageType1[which(is.na(combined$GarageType))] <- "None"
combined$GarageType <- as.factor(combined$GarageType1)
combined <- subset(combined,select = -GarageType1)

# Changing NA in GarageYrBlt to None
combined$GarageYrBlt[which(is.na(combined$GarageYrBlt))] <- 0 

# Changing NA in GarageFinish to None
combined$GarageFinish1 <- as.character(combined$GarageFinish)
combined$GarageFinish1[which(is.na(combined$GarageFinish))] <- "None"
combined$GarageFinish <- as.factor(combined$GarageFinish1)
combined <- subset(combined,select = -GarageFinish1)

# Changing NA in GarageQual to None
combined$GarageQual1 <- as.character(combined$GarageQual)
combined$GarageQual1[which(is.na(combined$GarageQual))] <- "None"
combined$GarageQual <- as.factor(combined$GarageQual1)
combined <- subset(combined,select = -GarageQual1)

# Changing NA in GarageCond to None
combined$GarageCond1 <- as.character(combined$GarageCond)
combined$GarageCond1[which(is.na(combined$GarageCond))] <- "None"
combined$GarageCond <- as.factor(combined$GarageCond1)
combined <- subset(combined,select = -GarageCond1)

# Changing NA in BsmtQual to None
combined$BsmtQual1 <- as.character(combined$BsmtQual)
combined$BsmtQual1[which(is.na(combined$BsmtQual))] <- "None"
combined$BsmtQual <- as.factor(combined$BsmtQual1)
combined <- subset(combined,select = -BsmtQual1)

# Changing NA in BsmtCond to None
combined$BsmtCond1 <- as.character(combined$BsmtCond)
combined$BsmtCond1[which(is.na(combined$BsmtCond))] <- "None"
combined$BsmtCond <- as.factor(combined$BsmtCond1)
combined <- subset(combined,select = -BsmtCond1)

# Changing NA in BsmtExposure to None
combined$BsmtExposure1 <- as.character(combined$BsmtExposure)
combined$BsmtExposure1[which(is.na(combined$BsmtExposure))] <- "None"
combined$BsmtExposure <- as.factor(combined$BsmtExposure1)
combined <- subset(combined,select = -BsmtExposure1)

# Changing NA in BsmtFinType1 to None
combined$BsmtFinType11 <- as.character(combined$BsmtFinType1)
combined$BsmtFinType11[which(is.na(combined$BsmtFinType1))] <- "None"
combined$BsmtFinType1 <- as.factor(combined$BsmtFinType11)
combined <- subset(combined,select = -BsmtFinType11)
# Changing NA in BsmtFinType2 to None
combined$BsmtFinType21 <- as.character(combined$BsmtFinType2)
combined$BsmtFinType21[which(is.na(combined$BsmtFinType2))] <- "None"
combined$BsmtFinType2 <- as.factor(combined$BsmtFinType21)
combined <- subset(combined,select = -BsmtFinType21)

# Changing NA in Electrical to None
combined$Electrical1 <- as.character(combined$Electrical)
combined$Electrical1[which(is.na(combined$Electrical))] <- "None"
combined$Electrical <- as.factor(combined$Electrical1)
combined <- subset(combined,select = -Electrical1)
```

```{r}
levels(combined$MSZoning) <- c(levels(combined$MSZoning),"None")
levels(combined$Utilities) <- c(levels(combined$Utilities),"None","NoSeWa")
levels(combined$Exterior1st) <- c(levels(combined$Exterior1st),"None","ImStucc","Stone")
levels(combined$Exterior2nd) <- c(levels(combined$Exterior2nd),"None","Other")
levels(combined$KitchenQual) <- c(levels(combined$KitchenQual),"None")
levels(combined$Functional) <- c(levels(combined$Functional),"None")
levels(combined$SaleType) <- c(levels(combined$SaleType),"None")
```


```{r}
Column_classes <- sapply(names(combined),function(x){class(combined[[x]])})
numeric_columns <-names(Column_classes[Column_classes != "factor"])
#determining skew of each numric variable
skew <- sapply(numeric_columns,function(x){skewness(combined[[x]],na.rm = T)})
# Let us determine a threshold skewness and transform all variables above the treshold.
skew <- skew[skew > 0.75]

# transform excessively skewed features with log(x + 1)
for(x in names(skew)) {
  combined[[x]] <- log(combined[[x]] + 1)
}
```
























